%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Regina Lauless} \\ \vspace{5pt}
    \small \faPhone* \texttt{989.859.2536} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{regina.lauless@email.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{U.S. Citizen}
    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Merck}{Nov. 2021 -- Present}
      {Solution Architect}{Minneapolis, MN}
      \resumeItemListStart
        \resumeItem{Implemented Apptio Targetprocess, connecting work to company goals. Piloted in 9 divisions, gathered feedback from sponsors and stakeholders, managed vendor relations and \textbf{implemented customer feedback loop, resulting in 15\% increase in customer satisfaction ratings}}
         \resumeItem{Scrum Master for End-to-End Financial Process Mapping team. \textbf{Increased team delivery by 75\%} by breaking down stories, coaching the team through defining the definition of done, and bringing in stakeholders for planning sessions and demos}
        \resumeItem{\textbf{Product owner and led develoment} of an OKR entry tool, simplifying processes and increasing user-friendliness, resulting in 20\% increase in user adoption}
        \resumeItem{OKR Champion, helping IT areas organize and articulate their goals and break them down into objectives and key results}
       
      \resumeItemListEnd

    \resumeSubheading
      {Target}{Oct. 2019 -- Feb. 2021}
      {Lead Software Engineer}{Minneapolis, MN}
      \resumeItemListStart
        \resumeItem{Increased guest cybersecurity awareness by designing, planning, and building security.target.com, an educational and informational site reaching millions of guests}
        \resumeItem{Product owner and developer for a core operations dashboard to view the health of company security and identify risks \textbf{increasing security compliance by 25\%}}
    \resumeItemListEnd

    \resumeSubheading
      {Merck}{Feb. 2019 -- Oct. 2019}
      {Full Stack Developer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Product Owner for a marketing journey mapping tool. Introduced Agile to non-IT business partners, conducted market and customer research, and built product roadmap. \textbf{MVP drove 25\% boost in marketing performance}}
        \resumeItem{Developed \textbf{W3C compliant WordPress themes} for consumer-facing sites, yielding millions of page views in multiple markets }
      \resumeItemListEnd
      
    \resumeSubheading
      {Merck}{Nov. 2017 -- Feb. 2019}
      {Solution Engineer}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed a project and program enterprise planning tool that \textbf{reduced financial errors by 25\%} in its first quarter}
        \resumeItem{Mentored students through data science project, resulting in improved understanding of key health factors. Tutored on best practices and provided career advice for over \textbf{100 students}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Western Govenors University}{expected May 2025}
      {Masters of Business Administration - Information Technology Managment}{}
      	\resumeItemListStart

        \resumeItemListEnd
    \resumeSubheading
      {Oregon State University}{}
      {BS Computer Science}{}
    \resumeSubheading
      {Michigan State University}{}
      {BS Medical Technology}{}
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Technology} {: Python, Ruby, JavaScript (React.js), HTML/CSS, SQL (PostgreSQL, MySQL), API Integration}\vspace{2pt} \\
     \textbf{Product}     {: Product Roadmaps, User Experience, Process Optimization, Stakeholder Management, Vendor Management, Cross-Team Collaboration, W3C Web Accessibility, Servant Leader}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
